---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "70%"
)
```
# ggVennDiagram

<!-- badges: start -->
<!-- badges: end -->

The goal of ggVennDiagram is to draw venn diagram in ggplot style.

## Installation

You can install the released version of ggVennDiagram from [CRAN](https://CRAN.R-project.org) with (under evaluation in CRAN):

``` r
install.packages("ggVennDiagram")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gaospecial/ggVennDiagram")
```
## Example

`ggVennDiagram` maps the fill color of each region to quantity, allowing us to visually observe the differences between different parts. 

```{r example}
library(ggVennDiagram)
genes <- paste("gene",1:1000,sep="")
set.seed(20190708)
x <- list(A=sample(genes,300),B=sample(genes,525),C=sample(genes,440),D=sample(genes,350))

# four dimension venn plot
ggVennDiagram(x)

# three dimension venn plot
ggVennDiagram(x[1:3])

# two dimension venn plot
ggVennDiagram(x[1:2])
```

`ggVennDiagram` return a ggplot object, which can be further modified with `ggplot` functions.

```{r}
library(ggplot2)
ggVennDiagram(x) + scale_fill_gradient(low="blue",high = "red")

ggVennDiagram(x,lty="dashed",color="black",size=2) + scale_fill_gradient(low="white",high = "red")
```

`ggVennDiagram` now support 2-4 dimension venn plot. The generated figure is generally ready for publish. The main function `ggVennDiagram()` will check how many items in the first paramenter and call corresponding function automatically.

The parameter `category.names` reprents set names. And the parameter `label` can label how many items are included in each parts.

```{r}
ggVennDiagram(x,category.names = c("Stage 1","Stage 2","Stage 3", "Stage4"))

ggVennDiagram(x,category.names = c("Stage 1","Stage 2","Stage 3", "Stage4"), label = NULL)
```


