---
title: "Fully Customed Venn Diagram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fully Customed Venn Diagram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggVennDiagram)
```

## Comprehensive customization by using helper functions

The main function `ggVennDiagram()` accepts a list input, and output a ggplot object. 
By measuring the length of input list, it automatically applies internal functions 
to build a plot in two steps: data preparation and visualization. 

Data preparation was packaged into one function `process_data()`. Its output
is a S4 `VennPlotData` class object, which contains three slots, `setEdge`, 
`setLabel` and `region`. These slot data then can be further plotted with `ggplot` 
functions. 

See below for a better understanding.

Generate example data.

```{r}
genes <- paste0("gene",1:1000)
set.seed(20231214)
gene_list <- list(A = sample(genes,100),
                  B = sample(genes,200),
                  C = sample(genes,300),
                  D = sample(genes,200))
```


```{r}
library(ggVennDiagram)
library(ggplot2)
```

Then we can reproduce the plot of `ggVennDiagram()` with several lines.

```{r}
venn <- Venn(gene_list)
data <- process_data(venn)
ggplot() +
  # 1. region count layer
  geom_polygon(aes(X, Y, fill = count, group = id), 
          data = venn_regionedge(data)) +
  # 2. set edge layer
  geom_path(aes(X, Y, color = id, group = id), 
          data = venn_setedge(data), 
          show.legend = FALSE) +
  # 3. set label layer
  geom_text(aes(X, Y, label = name), 
               data = venn_setlabel(data)) +
  # 4. region label layer
  geom_label(aes(X, Y, label = count), 
                data = venn_regionlabel(data)) +
  coord_equal() +
  theme_void()
```

The variable `data` is a structured list that has three slots.

```{r}
data
```


`ggVennDiagram` export functions to get these data, and they can be used 
for comprehensive customization in user-side.

- `Venn()`: Venn object constructor, use this to construct a Venn object from list.
- `process_data()`: process data with a Venn object
- `venn_regionedge()`: get region edge data to plot
- `venn_regionlabel()`: get region label position to plot
- `venn_setedge()`: get setedge data to plot
- `venn_setlabel()`: get setlabel data to plot


For example, you may change edge/fill/label properties as you will.

```{r}
ggplot() +
  # change mapping of color filling
  geom_polygon(aes(X, Y, fill = id, group = id), 
          data = venn_regionedge(data),
          show.legend = FALSE) +
  # adjust edge size and color
  geom_path(aes(X, Y, color = id, group = id), 
          data = venn_setedge(data), 
          linewidth = 3,
          show.legend = FALSE) +
  # show set label in bold
  geom_text(aes(X, Y, label = name), 
            fontface = "bold",
            data = venn_setlabel(data)) +
  # add a alternative region name
  geom_label(aes(X, Y, label = id), 
             data = venn_regionlabel(data),
             alpha = 0.5) +
  coord_equal() +
  theme_void()
```

