---
title: "Using New Shapes in Venn Diagram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using-new-shapes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(ggVennDiagram)
```

## Internal Shapes

The **ggVennDiagram** package has a set of built-in shapes that are used to plot
Venn diagram. These internal data are stored as sys data as a tibble. It can be
viewed with `ggVennDiagram:::shapes` and plotted with the function `plot_shapes()`.

```{r}
ggVennDiagram:::shapes
library(ggplot2)
```
The format of these shapes data are defined as followings:

**a tibble with 6 columns**

- `nsets`: number of sets, from 1-7.

- `type`: ellipse, circle or triangle

- `shape_id`: to separate different shapes

- `component`: each shape has two components, 'setEdge' and 'setLabel'

- `id`: to separate edges/labels of a shape. For example, 4 sets shape will have ids of 1-4.

- `xy`: coordinates


```{r}
plot_shapes()
```

## Using alternative internal shapes

By default, only the most appropriate shape is used when calling the main function
`ggVennDiagram()`. However, it may be specified in step wise plot which has been
described in [fully customed plot](./fully-customed).

For example:


```{r}
# Generate example data.
genes <- paste0("gene",1:1000)
set.seed(20210701)
gene_list <- list(A = sample(genes,100),
                  B = sample(genes,200),
                  C = sample(genes,300),
                  D = sample(genes,200))

# construct a Venn object
venn = Venn(gene_list)
data = process_data(venn, shape_id == "401")

ggplot() +
  geom_sf(aes(fill = count), data = venn_region(data)) +
  geom_sf(aes(color = id), data = venn_setedge(data), show.legend = FALSE) +
  geom_sf_text(aes(label = name), data = venn_setlabel(data)) +
  geom_sf_label(aes(label = count), data = venn_region(data)) +
  theme_void()
```

## Using a novel shape

Besides, user can use a novel shape when knows its coordinates. A possible start
is from a SVG shape. Therefore, I would like to show the method of using a 
novel triangle shape to plot 6-sets Venn diagram in this section.

The triangle is found in WiKi at https://upload.wikimedia.org/wikipedia/commons/5/56/6-set_Venn_diagram_SMIL.svg.

```{r echo=FALSE}
# I have to use a copy here
svg_url = "https://vnote-1251564393.cos.ap-chengdu.myqcloud.com/typora-img/triangles.svg"
knitr::include_graphics(svg_url)
```

Since SVG is a XML format file, the coordinates can be found in its content.
For this figure, the definition of six triangles are stored in the six object,
`object1b`, `object2b`, ..., `object6b`. We just need to build set regions by
closing the vertexes with the function `triangle()`.

```{r}
# the vertext coordinates of six triangles
vertex_coordinates <- list(c(-69277,-32868,135580,121186, 70900,199427),
                   c( 81988,-44426, 38444,206222,121044,165111),
                   c(203271,  9619, 39604, 82683, 84652,206669),
                   c(333561,225349, 61764, 76805, 38980,182461),
                   c(131886,385785, 38136,111491, 94208, 24690),
                   c(-60184,274046,142476, 39903,103276,183962))

triangles <- lapply(vertex_coordinates, triangle)
```

Likewise, `label_position()` is used to setup the coordinates of set labels.

```{r}
position <- tibble::tribble(
      ~x,       ~y,
      -50000,     50000,
      60000,          0,
      160000,     20000,
      280000,    170000,
      140000,    300000,
      -20000,   270000
    )
label_position = label_position(position)
```

Then construct a `VennPlotData` class object with shapes and labels.

```{r}
shape = VennPlotData(setEdge = triangles,
                     setLabel = label_position)

```

Now we can join plot data with set and calculated region values with `plotData_add_venn()`.


```{r}
genes <- paste0("gene",1:1000)
set.seed(20210701)
x <- list(A = sample(genes,100),
          B = sample(genes,150),
          C = sample(genes,200),
          D = sample(genes,250),
          E = sample(genes,300),
          F = sample(genes,350))
venn = Venn(x)

data = plotData_add_venn(plotData = shape, venn = venn)
```

and plot Venn diagram with ggplot2.

```{r}
ggplot() +
  geom_sf(aes(fill = count), data = venn_region(data)) +
  geom_sf(aes(color = name), size = 2, data = venn_setedge(data)) +
  geom_sf_text(aes(label = name), data = venn_setlabel(data)) +
  theme_void() +
  labs(color = "Set Name", fill = "Count")
```

