---
title: "Using New Shapes in Venn Diagram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using New Shapes in Venn Diagram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(ggVennDiagram)
```

## Internal Shapes

The **ggVennDiagram** package has a set of built-in shapes that are used to plot
Venn diagram. These internal data are stored as sys data as a tibble. It can be
accessed with `ggVennDiagram:::shapes` and viewed by the function `get_shapes()`, 
and plotted with the function `plot_shapes()`.

```{r}
shape1 = ggVennDiagram:::shapes[[4]]
shape1
```
The format of these shapes data are defined in `VennPlotData` class. Use `?VennPlotData` to view the document.

```{r}
plot_shape_edge(shape1)
```

`get_shapes()` will extract the meta features of these shapes and output a tibble. These information can be used for sepecifying a shape either by its id, or type.

```{r}
get_shapes()
```

For example, if you want to extract the shape whose id is "401f". This time we use `ggplot2` functions to plot the set edge of it.

```{r}
library(ggplot2)
shape2 = get_shape_by_id("401f")
plot_shape_edge(shape2)
```

The `plot_shapes()` function can be used to plot all the available shapes stored in this package.


```{r}
plot_shapes()
```

## Using alternative internal shapes

By default, only the most appropriate shape is used when calling the main function
`ggVennDiagram()`. However, it may be specified in step wise plot which has been
described in [fully customed plot](https://gaospecial.github.io/ggVennDiagram/articles/fully-customed).

For example:


```{r}
# Generate example data.
genes <- paste0("gene",1:1000)
set.seed(20210701)
gene_list <- list(A = sample(genes,100),
                  B = sample(genes,200),
                  C = sample(genes,300),
                  D = sample(genes,200))

# construct a Venn object
venn = Venn(gene_list)
data = process_data(venn, shape_id = "402")
plot_venn(data)
```

## Using a novel shape

If user knows the coordinates of a novel shape, it may also be used to draw in 
`ggVennDiagram`. The functions of this part have been transfered to a new R package 
`shapeMageR`, which can be found in <https://github.com/gaospecial/shapeMageR>.
To do this, the dependency of `ggVennDiagram` is very light, thus increase the 
accessiblity of the package.
