---
title: "Venn Plot with More Than Four Sets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Venn Plot with More Than Four Sets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ggVennDiagram)
library(ggplot2)
```

## Venn Diagram for more than four sets

With **ggVennDiagram** version less than 1.0, it only support 2-4 set Venn.
By importing the polygon from `venn` , `ggVennDiagram` now supports 5-7 sets Venn.

```{r}
genes <- paste0("gene",1:1000)
set.seed(20210507)
x <- list(A = sample(genes,100),
          B = sample(genes,150),
          C = sample(genes,200),
          D = sample(genes,250),
          E = sample(genes,300),
          F = sample(genes,350),
          G = sample(genes,400))
```


```{r}
ggVennDiagram(x, label = "none", edge_size = 1) + scale_fill_distiller(palette = "RdBu")
ggVennDiagram(x[1:6], label = "none", edge_size = 1) + scale_fill_distiller(palette = "RdBu")
ggVennDiagram(x[1:5], label = "none", edge_size = 1) + scale_fill_distiller(palette = "RdBu")
```

Although **ggVennDiagram** supports 5-7 sets Venn diagram, I don't encourage to
use them in scientific publications as it  is difficult to separate the border 
of different sets in the plot (even with thick edges), especially for 7 and 6 sets Venn.
Upset plot is a possible solution for these datasets. You may check a discussion of
the [Applications of Venn, Euler and Upset plot](https://venn.bio-spring.top/applications.html).

## Upset plot is natively supported in ggVennDiagram 1.5

